Phylogeographic inference with microtellite and SNPs

### 2019-06-28 code/rmarkdown/article.Rmd
table 1

---
title: "Phylogeographic inference with microtellite and SNPs"
author: |
  | Miguel Camacho-Sanchez${\ast^1}$, Guillermo Velo-Antón$^{1}$, Ana Veríssimo$^1$, Silvia Carvalho$^2$
  | $^1$ CIBIO/InBIO, Centro de Investigação em Biodiversidade e Recursos Genéticos da Universidade do Porto, Vairão, Portugal
  | Correspondence should be addressed to miguelcamachosachez@gmail.com
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  rmarkdown::pdf_document:
    toc: false
    keep_tex: true
    fig_caption: yes
    includes:
      in_header: preamble.tex
fontsize: 11pt
documentclass: article
subparagraph: true
---

>>>>

---
title: "Phylogeographic inference with microtellite and SNPs"
author: |
  | Miguel Camacho-Sanchez${\ast^1}$, Guillermo Velo-Antón$^{1}$, Ana Veríssimo$^1$, Silvia Carvalho$^2$
  | $^1$ CIBIO/InBIO, Centro de Investigação em Biodiversidade e Recursos Genéticos da Universidade do Porto, Vairão, Portugal
  | Correspondence should be addressed to miguelcamachosachez@gmail.com
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document: default
  pdf_document: default
---
